%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\setdescription{leftmargin=2cm,labelindent=1cm}

\name{Balázs Varga}
\address{+3600~$\cdot$~000~$\cdot$~0000 \\ Skype: - \\
\href{mailto:-@gmail.com}{-@gmail.com}}
\address{- \\ H-1000 Budapest \\ Hungary}

\begin{document}

\begin{rSection}{About}
 Birth: 01/01/1970 \\
 \\
 Enthusiastic about Clean Code, DevOps culture and Agile methodologies. Likes to work
 with open source technologies and contribute to the community with knowledge and code.
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work experience}

\begin{rSubsection}{Digital Natives Ltd.}
{2014 - Present}{Software engineer}{Budapest}
\item I design and develop custom applications following Agile methods and I do system integration.
\item Projects:
	\begin{description}
		\item[Elegran] \hfill \\
		I plan and develop features into the datahub backend for Elegran’s real estate portals.
		Logins into the applications are handled by the CAS SSO solution. \\
		Technology: Ruby, Rails, MongoDB, Redis, PostgreSQL, CAS
	\end{description}
	\begin{description}
		\item[Greenfox Academy] \hfill \\
		An education program for early coders to become junior developers.
		On the other hand, this is a recruit channel for IT companies who are hungry
		for young, talented developers. \\
		My responsibilities are to participate in design the curriculum, teach
		programming concepts, devops and organize coding dojos.
	\end{description}
\end{rSubsection}

\begin{rSubsection}{Red Hat EMEA}
{July 2014 – August 2014}{Software Engineer Intern}{Brno, Czech Republic}
\item Projects:
	\begin{description}
		\item[OpenShift Origin - Platform as a service (PaaS)] \hfill \\
		I worked in the Developer Experience team. I fixed issues with the current version
		and participated in the R\&D work of the product's next generation.\\
		My main task was to start the research on how to handle logs generated by the containers
		in a scaleable way. \\
		Technology: Kubernetes, Linux, Docker, Go
	\end{description}
\end{rSubsection}

\begin{rSubsection}{INBUSS Ltd.}
{2011 - 2014}{Software engineer}{Budapest}
\item I designed and developed custom applications, customized existing solutions, provided support for sysadmins and developers.
\item Projects:
	\begin{description}
		\item[Feasibility study: migration from OpenSSO to OpenAM] \hfill \\
		I made a study for a Hungarian telecommunnications company on the migration their old Sun OpenSSO based
		Single-Sign-On solution to ForgeRock OpenAM.
		One of the key challenges was to handle all dependencies and create a schedule for the project.
		\item[Sun OpenSSO] \hfill \\
		I provided support for developers and sysadmins, I created and maintained custom modules for
		a Hungarian telecommunications company. I supervised the process of new systems'
		integration in the SSO federation with policy agents and web services.
		\item[Photo printing terminal software] \hfill \\
		My task was to plan and create a JavaFX client application to run on Atom based PCs.
		The main challenge was to solve the communication with low level components such as: photo printer,
		coin acceptor and coin router. \\
		Technology: C, C++, libusb, Java, JavaFX, ImageMagick
		\item[Negoma webshop] \hfill \\
		My tasks were to refactor, design and develop new features into a 10 years old project. \\
		Technology: JavaEE, Hibernate, Tapestry 4, Perl, Javascript, JQuery, XML, Maven, PostgreSQL
		\item[DIDb - Driver Identification Database] \hfill \\
		DIDb is a service to keep records of truck drivers and their shipments.
		My task was to extend the existing solution with new functionalities.
		I also migrated the whole project structure from Ant to Maven. \\
		Technology: JavaEE, Java Webstart, Hibernate, Swing, Maven, Glassfish Metro,
		PostgreSQL
	\end{description}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Simonyi Károly College for Advanced Studies}
{2009 - 2014}{Project manager, software developer, sysadmin}{Budapest}
\item 2013-2014 - helped on international professional conferences (MLOC.js and RAMP)
\item Projects:
	\begin{description}
		\item[OpenAM and OpenDJ] \hfill \\
		We provided Single-Sign-On with OpenAM for the community webapplications on the faculty.
		I maintained the solution and developed custom database authentication module.
		I helped to integrate	new apps into the service with Shibboleth Service Provider
		and Policy Agents.
		\item[VIR Profile and Groups] \hfill \\
		It is a register for the university students which also keeps records of
		their activities in the community. I was the project manager and one of the
		maintainers. \\
		\url{https://github.com/kir-dev/korok} \\
		Technology: JavaEE, Hibernate, Wicket, SOAP, PostgreSQL
		\item[Address Book for internal use] \hfill \\
	  Participated in architecting and developing a new application for the college
	  organization which can store alumni data and their work history in the groups.
	  The major challenge was to make a smart search with a simple UI. \\
	  \url{https://github.com/kir-dev/simonyi-cimtar} \\
		Technology: Ruby, Rails, JQuery, Shibboleth SP, Apache2, Passenger, PostgreSQL
		\item[Printer.sch] \hfill \\
		It is a service which lists all online printers in the dormitory. \\
		Based on my idea, we made a simple PHP frontend and a Python client to enable students
		to share their printers. \\
		\url{https://github.com/kir-dev/printer} \\
		Technology: PHP, MySQL, Shibboleth SP
	\end{description}
\end{rSubsection}

%------------------------------------------------

\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Studies}

{\bf Budapest University of Technology and Economics, Hungary} \hfill {2008 - 2014} \\
Software Engineering B.Sc. (not graduated) \smallskip
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Language skills & English, Hungarian (native speaker) \\
Programming languages & Java (++), Ruby (+++), JS (+), C/C++ (+) \\
Protocols \& APIs & TCP/IP basics, XML, JSON, SOAP, SAML, REST \\
Databases & PostgreSQL, MongoDB, Redis \\
Frameworks & Rails, JavaEE \\
Application servers & JBoss / Wildfly, Glassfish, Tomcat \\
Tools & git, Docker, Sublime / Atom, Linux, Maven
\end{tabular}
\end{rSection}

\begin{rSection}{Blog and profiles}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Blog & \url{http://blog.vbalazs.me} \\
Github & \url{http://git.vbalazs.me} \\
More profiles & \url{http://vbalazs.me}
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
